Bridging [TBD]

### 2014-03-19 paper/draft.tex
Updated bibliography.

% !TEX TS-program = pdflatex
% !TEX encoding = UTF-8 Unicode

% This is a simple template for a LaTeX document using the "article" class.
% See "book", "report", "letter" for other types of document.

\documentclass{sig-alternate}
%\usepackage[margin={1.5cm,3cm}]{geometry}
%\setlength{\columnsep}{1cm}
\usepackage[utf8]{inputenc} % set input encoding (not needed with XeLaTeX)

%%% Examples of Article customizations
% These packages are optional, depending whether you want the features they provide.
% See the LaTeX Companion or other references for full information.

%%% PAGE DIMENSIONS
%\usepackage{geometry} % to change the page dimensions
%\geometry{a4paper} % or letterpaper (US) or a5paper or....
% \geometry{margin=2in} % for example, change the margins to 2 inches all round
% \geometry{landscape} % set up the page for landscape
%   read geometry.pdf for detailed page layout information
%\usepackage[hidelinks]{hyperref}
%\usepackage[autostyle,french=guillemets,babel]{csquotes}
\usepackage{graphicx} % support the \includegraphics command and options
\usepackage[backend=biber]{biblatex}
\addbibresource{biblio.bib}
% \usepackage[parfill]{parskip} % Activate to begin paragraphs with an empty line rather than an indent
%%% PACKAGES
\usepackage{booktabs} % for much better looking tables
\usepackage{array} %
% for better arrays (eg matrices) in maths
\usepackage{paralist} % very flexible & customisable lists (eg. enumerate/itemize, etc.)
\usepackage{verbatim} % adds environment for commenting out blocks of text & for better verbatim
%\usepackage{subfig} % make it possible to include more than one captioned figure/table in a single float
% These packages are all incorporated in the memoir class to one degree or another...
\usepackage{amsfonts}

%%% HEADERS & FOOTERS
\usepackage{fancyhdr} % This should be set AFTER setting up the page geometry
\pagestyle{fancy} % options: empty , plain , fancy
\renewcommand{\headrulewidth}{0pt} % customise the layout...
\lhead{}\chead{}\rhead{}
\lfoot{}\cfoot{\thepage}\rfoot{}

%%% SECTION TITLE APPEARANCE
%\usepackage{sectsty}
%\allsectionsfont{\sffamily\mdseries\upshape} % (See the fntguide.pdf for font help)
%% (This matches ConTeXt defaults)

%%% ToC (table of contents) APPEARANCE
%\usepackage[nottoc,notlof,notlot]{tocbibind} % Put the bibliography in the ToC
%\usepackage[titles,subfigure]{tocloft} % Alter the style of the Table of Contents
%\renewcommand{\cftsecfont}{\rmfamily\mdseries\upshape}
%\renewcommand{\cftsecpagefont}{\rmfamily\mdseries\upshape} % No bold!

%%% END Article customizations

%%% The "real" document content comes below...

\title{ Bridging [TBD]}

\author{
% You can go ahead and credit any number of authors here,
% e.g. one 'row of three' or two rows (consisting of one row of three
% and a second row of one, two or three).
%
% The command \alignauthor (no curly braces needed) should
% precede each author name, affiliation/snail-mail address and
% e-mail address. Additionally, tag each line of
% affiliation/address with \affaddr, and tag the
% e-mail address with \email.
%
% 1st. author
\numberofauthors{3}
\alignauthor
Alex Palesandro\\
\affaddr{Orange Labs, France}\\
\texttt{alex.palesandro@gmail.com}
\alignauthor
Aurélien Wailly\\
\affaddr{Orange Labs, France}\\
\texttt{aurelien.wailly@orange.com}
\alignauthor
Marc Lacoste\\
\affaddr{Orange Labs, France}
\texttt{marc.lacoste@orange.com}
}
%\setlist[itemize]{leftmargin=*}
\begin{document}
\maketitle

@@

\section{Introduction}
\label{ref:intro}
Cloud computing platform are a solid reality nowadays. Modern cloud platforms are able to provide elastic use of resources, optimizing their allocation in order to meet the user needings. However, currently deployed cloud platforms present still several limitation.

@@

This paper is organized as following. In Section~\ref{sec:rw} we analyze the nested virtualization ecosystem and position existing solutions regarding our design principles. In Section~\ref{classic}, we details limitations of classical nested virtualization approach and in Section~\ref{sec:mh} we present the microvisor approach. In Section~\ref{sec:archcomp} we compare cloud architectures propositions, combining nested virtualization and microvisors, leveraging the design principles grid introduced before.
%Furthermore, in Section 6 we define a security architecture for multi-cloud scenario, with an analysis of necessary software components to satisfy vertical design principles.
In Section~\ref{sec:conclu}, we conclude the paper with future works and our vision of the SuperCloud.
% in section in section 6 we define a security architecture for multi-cloud scenario, with an analysis of necessary software components to satisfy vertical design principles. In section 8, we conclude the paper with future works in section 8.

\section{Related Work}
\label{sec:rw}
% Intro + performance issues
Several works presented in literature integrates these a subset of this design principles in their architecture, leveraging nested virtualization \cite{turtle:ibm,art:blan, cloudvisor:zhang}
Cloud computing feature set could be enlarged exploiting two layers of virtualization instead of just one. The presence of two different hypervisors allows the possibility to specialize hypervisors functions. Instead of having a general purpose hypervisor we could split the hypervisor role in two different layers, interconnected with a well defined interface.
Each layer will have to care about a subset of features, simplifying overall development.
However, nested virtualization on x86 architecture faced impeding performance issues \cite{rec:virt}.

@@

Other approaches leveraging only one layer of virtualization does not achieve the whole design-principle satisfaction. Self-service cloud approach (SSC) \cite{ssc:art} design a complete security architecture to overcome major security and privacy issues of currently deployed cloud infrastructures, in order to alleviate the different needing user-centric and provider-centric vision of cloud computing presented in \ref{par:intro}. Even if this architecture reproduces an approach similar to the SuperCloud without leveraging an extra layer of virtualization (DP4), the approach changes the behavior where the user acts introducing new components that have to be directly managed by the user. Therefore, the main drawback of this solution is to change the interface with the user, preventing the possibility to straightforwardly move to the new platform without having to change its applications (DP5).

@@

Introducing nested virtualization, we have to identify the two main actors involved in the virtualization process: bare-metal hypervisor (L0) and nested hypervisor (L1). In addition, we will refer to the nested guest as L2 guest. 
However, virtualization introduces a computational overhead. It is small when we are dealing with single layer virtualization, but it grows exponentially when we try to add further levels \cite{rec:virt}. This huge performance overhead has prevented nested virtualization adoption during last years and had been finally addressed by Ben Yehuda et Al \cite{turtles:ibm} proposing an architecture with acceptable overhead.

Nested virtualization feasibility opened a plenty of new possibilities and perspectives, that have been largely discussed in literature \cite{rec:virt,turtles:ibm,art:blan}. The first aspect in common among different works proposed in literature is to diversify hypervisor functions, introducing new features but keeping the existing ones. In a general analysis of existing works, it could be possible to identify the general role of each different layer.
On one hand, L0 is charged of the vertical aspects of the platform. It has to achieve  the best possible performances and enforcing the strongest possible level of isolation. L0 represents the last line of defense of the platform and a privileged point of global status observation.

@@

%\section{Conclusion}
%{\scriptsize
%\bibliographystyle{abbrv}
%\bibliography{biblio}
%}
\end{document}

>>>>

\documentclass{sig-alternate}
\usepackage[utf8]{inputenc} 
%\usepackage[hidelinks]{hyperref}
%\usepackage[autostyle,french=guillemets,babel]{csquotes}
\usepackage{graphicx} % support the \includegraphics command and options
%\usepackage[backend=biber]{biblatex}
%\addbibresource{biblio.bib}
% \usepackage[parfill]{parskip} % Activate to begin paragraphs with an empty line rather than an indent
\usepackage{booktabs}
\usepackage{array} 
\usepackage{paralist} 
\usepackage{verbatim} 
\usepackage{amsfonts}
\usepackage{fancyhdr} 
%\pagestyle{fancy} 
%\renewcommand{\headrulewidth}{0pt} % customise the layout...
%\lhead{}\chead{}\rhead{}
%\lfoot{}\cfoot{\thepage}\rfoot{}

\title{Bridging [TBD]}

\author{
\numberofauthors{3}
\alignauthor
Alex Palesandro\\
\affaddr{Orange Labs, France}\\
\texttt{alex.palesandro@gmail.com}
\alignauthor
Aurélien Wailly\\
\affaddr{Orange Labs, France}\\
\texttt{aurelien.wailly@orange.com}
\alignauthor
Marc Lacoste\\
\affaddr{Orange Labs, France}
\texttt{marc.lacoste@orange.com}
}

\begin{document}
\maketitle

@@

\section{Introduction}
\label{sec:intro}

Cloud computing platform are a solid reality nowadays. Modern cloud platforms are able to provide elastic use of resources, optimizing their allocation in order to meet the user needings. However, currently deployed cloud platforms present still several limitation.

@@

This paper is organized as following. In Section~\ref{sec:rw} we analyze the nested virtualization ecosystem and position existing solutions regarding our design principles. In Section~\ref{sec:classic}, we details limitations of classical nested virtualization approach and in Section~\ref{sec:mh} we present the microvisor approach. In Section~\ref{sec:archcomp} we compare cloud architectures propositions, combining nested virtualization and microvisors, leveraging the design principles grid introduced before.
%Furthermore, in Section 6 we define a security architecture for multi-cloud scenario, with an analysis of necessary software components to satisfy vertical design principles.
In Section~\ref{sec:conclu}, we conclude the paper with future works and our vision of the SuperCloud.
% in section in section 6 we define a security architecture for multi-cloud scenario, with an analysis of necessary software components to satisfy vertical design principles. In section 8, we conclude the paper with future works in section 8.

\section{Related Work}
\label{sec:rw}

% Intro + performance issues
Several works presented in literature integrates these a subset of this design principles in their architecture, leveraging nested virtualization \cite{turtle:ibm,art:blan, cloudvisor:zhang}
Cloud computing feature set could be enlarged exploiting two layers of virtualization instead of just one. The presence of two different hypervisors allows the possibility to specialize hypervisors functions. Instead of having a general purpose hypervisor we could split the hypervisor role in two different layers, interconnected with a well defined interface.
Each layer will have to care about a subset of features, simplifying overall development.
However, nested virtualization on x86 architecture faced impeding performance issues \cite{rec:virt}.

@@

Other approaches leveraging only one layer of virtualization does not achieve the whole design-principle satisfaction. Self-service cloud approach (SSC) \cite{ssc:art} design a complete security architecture to overcome major security and privacy issues of currently deployed cloud infrastructures, in order to alleviate the different needing user-centric and provider-centric vision of cloud computing presented in \ref{sec:intro}. Even if this architecture reproduces an approach similar to the SuperCloud without leveraging an extra layer of virtualization (DP4), the approach changes the behavior where the user acts introducing new components that have to be directly managed by the user. Therefore, the main drawback of this solution is to change the interface with the user, preventing the possibility to straightforwardly move to the new platform without having to change its applications (DP5).

@@

Introducing nested virtualization, we have to identify the two main actors involved in the virtualization process: bare-metal hypervisor (L0) and nested hypervisor (L1). In addition, we will refer to the nested guest as L2 guest. 
However, virtualization introduces a computational overhead. It is small when we are dealing with single layer virtualization, but it grows exponentially when we try to add further levels \cite{rec:virt}. This huge performance overhead has prevented nested virtualization adoption during last years and had been finally addressed by Ben Yehuda et Al \cite{turtle:ibm} proposing an architecture with acceptable overhead.

Nested virtualization feasibility opened a plenty of new possibilities and perspectives, that have been largely discussed in literature \cite{rec:virt,turtle:ibm,art:blan}. The first aspect in common among different works proposed in literature is to diversify hypervisor functions, introducing new features but keeping the existing ones. In a general analysis of existing works, it could be possible to identify the general role of each different layer.
On one hand, L0 is charged of the vertical aspects of the platform. It has to achieve  the best possible performances and enforcing the strongest possible level of isolation. L0 represents the last line of defense of the platform and a privileged point of global status observation.

@@

{\scriptsize
\bibliographystyle{abbrv}
\bibliography{biblio}
}
\end{document}
